\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-12 paper.tex
caption for table

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{diazessay} % Font size (can be 10pt, 11pt or 12pt)
\usepackage{float}
\usepackage{sectsty}
\usepackage{appendix}
\usepackage[numbers]{natbib}
\sectionfont{\centering}
\usepackage{listings}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{fancyvrb}

@@

\VerbatimInput{evilstats.txt}

@@

The network traffic analysis uncovered the behavior over the wire of a host infected by a strain of ransomware known as Maktub. The host exhibited signs of compromise following interaction with a mail server, indicating a malicious mail attachment was the initial point of entry. The host established a openVPN session tunneled over TLS as a likely secure communication channel to the C2. Finally, in order to provide a payment platform for victim, the attackers used TOR hidden services over a .onion to the web link. These domains obtained via DNS quiries provided the final pieces in understanding the malware's bahavior and laying attribution to the Maktub locker.

>>>>

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
%%%%%%%%%never4getSINGAPOOR
\documentclass[11pt]{diazessay} % Font size (can be 10pt, 11pt or 12pt)
\usepackage{float}
\usepackage{sectsty}
\usepackage{appendix}
\usepackage[numbers]{natbib}
\sectionfont{\centering}
\usepackage{listings}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{fancyvrb}

@@

Table of TCP conversation with malware infrastructure.
\VerbatimInput{evilstats.txt}

@@

The network traffic analysis uncovered the behavior over the wire of a host infected by a strain of ransomware known as Maktub. The host exhibited signs of compromise following interaction with a mail server, indicating a malicious mail attachment was the initial point of entry. The host established a openVPN session tunneled over TLS as a likely secure communication channel to the C2. Finally, in order to provide a payment platform for victim, the attackers used TOR hidden services over a .onion to the web link. These domains obtained via DNS queries provided the final pieces in understanding the malware's bahavior and laying attribution to the Maktub locker.
